Source Summaries

### 2020-02-05 sourceSummaries.tex
Repaired Daniel's section and recompiled
Added Group Member Blockx
fixed ToC

\noindent
\section{Security Analysis of Bluetooth Technology}

\noindent
\subsection{Citation}

@@

\subsection{Main Idea}

@@

\subsection{Theory}

@@

\subsection{Method}

@@

\subsection{Findings}

@@

\subsection{Future Directions}

@@

\section{Extracting the Security Features Implemented in a Bluetooth LE Connection}

\noindent
\subsection{Citation}

@@

\subsection{Theory}

\subsection{Method}

@@

\section[Finding Vulnerabilities in IoT Devices: Ethical Hacking of Electronic Locks]{Finding Vulnerabilities in IoT Devices: Ethical \\Hacking of Electronic Locks}

\noindent
\subsection{Citation}

@@

\section{Security Evaluation and Exploitation of Bluetooth Low Energy Devices}

\noindent
\subsection{Citation}

>>>>

\section{Week 3}

\noindent
\subsection{Security Analysis of Bluetooth Technology}

\noindent
\subsubsection{Citation}

@@

\subsubsection{Main Idea}

@@

\subsubsection{Theory}

@@

\subsubsection{Method}

@@

\subsubsection{Findings}

@@

\subsubsection{Future Directions}

@@

\subsection{Extracting the Security Features Implemented in a Bluetooth LE Connection}

\noindent
\subsubsection{Group member}
Joshua Niemann
\subsubsection{Citation}

@@

\subsubsection{Theory}

\noindent
Game Theory is the primary theory being tested in this article.  The authors examine various versions of the Bluetooth protocol to determine which versions have the best security measures in place.  In addition, the authors analyze BLE devices in an effort to learn which devices and device manufacturers have the best security.

\subsubsection{Method}

@@

\subsection[Finding Vulnerabilities in IoT Devices: Ethical Hacking of Electronic Locks]{Finding Vulnerabilities in IoT Devices: Ethical \\Hacking of Electronic Locks}

\noindent
\subsubsection{Citation}

@@

\subsection{Security Evaluation and Exploitation of Bluetooth Low Energy Devices}

\noindent
\subsubsection{Citation}
